---
title: "Sentence Reading Task Results"
output: html_document
---
##  Andrés-Rojas (2022)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


```{r, include=FALSE}
library(here)
library(tidyverse)
library(kableExtra)

source(here("scripts", "05_load_data.R"))
```

### Overview

The purpose of this document is to provide a statistical analysis of the data of three participants segmented so far (Andrés Rojas, 2022). 
The primary research question investigated was whether there was a difference in rhotic production (both taps and trills) between a pre-test and post-test. 
The following analysis is for the 3 participants in the sentence reading task only. 
Overall, I took the following steps in the analysis:

1. I imported and tidyed the data. The scripts that I used is available in this github repo under `scripts/01_tidy_srt.R`. In addition to the script to tidy the data, I also wrote a function `run_t_test` to help run paired t-tests per participant that can be used later (and to more or less automate further analysis in this style). This function's source code can be found in this repo under `scripts/00_helpers.R`

2. I ran the scripts and analyzed the data to within this document, please see the results below:

### Results 

Overall, it looks like the training worked well for P3E, but not as much for the other two. 
Table 1 shows the mean duration of taps per participant during the pre and post tests, and Table 2 shows the same information for trills.
As you explained, if training is effective, tap duration should be lower at post test. 
This was reflected in the means of both P1E and P3E, but not P5E.
For trills, an increase in duration would suggest that the training was effective: this was only the case for P3E. 


```{r}
tap_df <- srt %>% 
  filter(!duration == "N/A" & !duration == "N/A /d/") %>% 
  group_by(participant, is_trill, time) %>% 
  filter(is_trill == "tap") %>% 
  summarize(mean = mean(as.numeric(duration))) %>% 
  pivot_wider(names_from = participant, values_from = mean) %>% 
  dplyr::select(time, P1E, P3E, P5E) %>% 
  arrange(desc(time)) 

tap_df$is_trill <- NULL

tap_df %>% 
  knitr::kable(digits = 2, caption = "Table 1: Average duration of tap productions during pre and post-tests per participant") %>% 
  kable_styling(full_width = FALSE)


```

In addition to mean comparisons, I did a series of paired t-tests. 
This test determines whether a mean difference can, within a 95% confidence interval, not be equal to zero by taking into account the variation in the response durations submitted to the model. That is, if there was greater deviation in the overall sample, a mean difference between pre and post tests would more likely be due to chance than if the values were more consistent. 
In general, t-tests are reported using this format in APA: 

*t(df) = t value, p = p value*

Df is degree of freedom 

```{r}

trill_df <- srt %>% 
  filter(!duration == "N/A" & !duration == "N/A /d/") %>% 
  group_by(participant, is_trill, time) %>% 
  filter(is_trill == "trill") %>% 
  summarize(mean = mean(as.numeric(duration))) %>% 
  pivot_wider(names_from = participant, values_from = mean) %>%
  dplyr::select(time, P1E, P3E, P5E) %>% 
  arrange(desc(time))

trill_df$is_trill <- NULL

trill_df %>% 
  knitr::kable(digits = 2, caption = "Table 2: Average duration of trill productions during pre and post-tests per participant") %>% 
  kable_styling(full_width = FALSE)

```



```{r}
srt_t_test <- read.csv(here("data", "tidy", "srt_t_tests.csv")) 
```


```{r}
srt_t_test %>%
  filter(tap_or_trill == "tap") %>% 
  select(Participant, p_val, t_val, estimate, ci_lo, ci_hi) %>% 
  knitr::kable(digits = 3, caption = "
Table 3: Results of Paired t-tests of taps comparing duration during pre and post tests") %>% 
  kable_styling(full_width = FALSE)

```



```{r}
srt_t_test %>%
  filter(tap_or_trill == "trill") %>% 
  select(Participant, p_val, t_val, estimate, ci_lo, ci_hi) %>% 
  knitr::kable(digits = 3, caption = "Table 4: Results of Paired t-tests of trills comparing duration during pre and post tests") %>% 
  kable_styling(full_width = FALSE)

```


**Figure 1: Productions of taps per participant during the pre and post test**
```{r, dpi = 300}

level_order <- c('PRE', 'POST')

srt %>% 
  filter(!duration == "N/A" & !duration == "N/A /d/") %>%
  filter(is_trill == "tap") %>% 
  ggplot(aes(x = factor(time, level = level_order), y = as.numeric(duration), color = is_trill)) + geom_boxplot(fill = "deepskyblue4", color = "black", outlier.size = 0) + 
  facet_wrap(~participant) + xlab("Test Time") + ylab("Rhotic Duration (ms)") +
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"),
        legend.position = "bottom") + theme(legend.position = "none")  + ggtitle("Taps")
```



**Figure 2: Productions of trills per participant during the pre and post test**
```{r, dpi = 300}


level_order <- c('PRE', 'POST')

srt %>% 
  filter(!duration == "N/A" & !duration == "N/A /d/") %>%
  filter(is_trill == "trill") %>% 
  ggplot(aes(x = factor(time, level = level_order), y = as.numeric(duration), color = is_trill)) + geom_boxplot(fill = "deepskyblue4", color = "black", outlier.size = 0) + 
  facet_wrap(~participant) + xlab("Test Time") + ylab("Rhotic Duration (ms)") +
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"),
        legend.position = "bottom") + theme(legend.position = "none") + ggtitle("Trills")
```


