---
title: "Spanish 203 Sentence Reading Task Results"
output: pdf_document
---
##  Andrés-Rojas (2022)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


```{r, include=FALSE}
library(here)
library(tidyverse)
library(kableExtra)

source(here("scripts", "05_load_data.R"))

srt = srt %>% 
  filter(level == "sp203")
```

### Overview

```{r}
tap_df <- srt %>% 
  filter(!duration == "N/A" & !duration == "N/A /d/") %>% 
  group_by(participant, is_trill, time) %>% 
  filter(is_trill == "tap") %>% 
  filter(duration != "23_126") %>% 
  summarize(mean = mean(as.numeric(duration))) %>% 
  pivot_wider(names_from = participant, values_from = mean) %>% 
  dplyr::select(time, P1E, P2E) %>% 
  arrange(desc(time)) 

tap_df$is_trill <- NULL

tap_df %>% 
  knitr::kable(digits = 2, caption = "Average duration of tap productions during pre and post-tests per participant") %>% 
  kable_styling(full_width = FALSE)


```

**Note**, for P2E, one observation was removed as it was coded as "23_126" and caused an error in the code. 
If this was in error, we can update the data file and re-run the code.

```{r}

trill_df <- srt %>% 
  filter(!duration == "N/A" & !duration == "N/A /d/") %>% 
  group_by(participant, is_trill, time) %>% 
  filter(is_trill == "trill") %>% 
  summarize(mean = mean(as.numeric(duration))) %>% 
  pivot_wider(names_from = participant, values_from = mean) %>%
  dplyr::select(time, P1E, P2E) %>% 
  arrange(desc(time))

trill_df$is_trill <- NULL

trill_df %>% 
  knitr::kable(digits = 2, caption = "Average duration of trill productions during pre and post-tests per participant") %>% 
  kable_styling(full_width = FALSE)

```


```{r}
srt_t_test_sp3 %>%
  filter(tap_or_trill == "tap") %>% 
  select(Participant, df, p_val, t_val, estimate, ci_lo, ci_hi) %>% 
  knitr::kable(digits = 3, caption = "Results of Paired t-tests of taps comparing duration during pre and post tests") %>% 
  kable_styling(full_width = FALSE)

```

Table 3 shows the results of each t-test in which tap duration production is compared from pre to post test. 
The results suggest that the duration of taps by participant P1E fell by 
`r srt_t_test_sp3$estimate[1] %>% round(digits = 2)*-1` (95% CI `r srt_t_test_sp3$ci_hi[1] %>% round(digits = 2)*-1` - `r srt_t_test_sp3$ci_lo[1] %>% round(digits = 2)*-1`), as determined by a paired t-test (t(`r srt_t_test_sp3$df[1]`) = `r srt_t_test_sp3$t_val[1] %>% round(digits = 3)`, p < .005).
The same trend was observed in P2E: tap duration decreased by `r srt_t_test_sp3$estimate[3] %>% round(digits = 2)*-1` (95% CI `r srt_t_test_sp3$ci_hi[3] %>% round(digits = 2)*-1` - `r srt_t_test_sp3$ci_lo[3] %>% round(digits = 2)*-1`), as determined by a paired t-test (t(`r srt_t_test_sp3$df[3]`) = `r srt_t_test_sp3$t_val[3] %>% round(digits = 3)`, p < .005)

```{r}
srt_t_test_sp3 %>%
  filter(tap_or_trill == "trill") %>% 
  select(Participant, df, p_val, t_val, estimate, ci_lo, ci_hi) %>% 
  knitr::kable(digits = 3, caption = "Results of Paired t-tests of trills comparing duration during pre and post tests") %>% 
  kable_styling(full_width = FALSE)

```

Table 4 shows an analogous analysis in trill production in which pre-test duration was compared to post-test duration. 
The results of the paired t-test were inconclusive for P1E, 
`r srt_t_test_sp3$estimate[2] %>% round(digits = 2)` (95% CI  `r srt_t_test_sp3$ci_lo[2] %>% round(digits = 2)` - `r srt_t_test_sp3$ci_hi[2] %>% round(digits = 2)`; t(`r srt_t_test_sp3$df[2]`) = `r srt_t_test_sp3$t_val[2] %>% round(digits = 3)`, p < .6).
On the other hand, P2E's trill duration increased by `r srt_t_test_sp3$estimate[4] %>% round(digits = 2)` (95% CI  `r srt_t_test_sp3$ci_lo[4] %>% round(digits = 2)` - `r srt_t_test_sp3$ci_hi[4] %>% round(digits = 2)`; t(`r srt_t_test_sp3$df[4]`) = `r srt_t_test_sp3$t_val[4] %>% round(digits = 3)`, p < .005).

### Plots

Here are a few boxplots by participant.
These plots show the distribution of responses per participant in both taps (Figure 1) and trills (Figure 2) between the pre and post tests. 


```{r}

level_order <- c('PRE', 'POST')

srt %>% 
  filter(!duration == "N/A" & !duration == "N/A /d/") %>%
  filter(is_trill == "tap") %>% 
  ggplot(aes(x = factor(time, level = level_order), y = as.numeric(duration), color = is_trill)) + geom_boxplot(fill = "deepskyblue4", color = "black", outlier.size = 0) + 
  ylim(0, 100) + 
  facet_wrap(~participant) + xlab("Test Time") + ylab("Rhotic Duration (ms)") +
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"),
        legend.position = "bottom") + theme(legend.position = "none") + ggtitle("Figure 1: Productions of taps per participant during the pre and post test")
```

```{r}


level_order <- c('PRE', 'POST')

srt %>% 
  filter(!duration == "N/A" & !duration == "N/A /d/") %>%
  filter(is_trill == "trill") %>% 
  ggplot(aes(x = factor(time, level = level_order), y = as.numeric(duration), color = is_trill)) + geom_boxplot(fill = "deepskyblue4", color = "black", outlier.size = 0) + 
  facet_wrap(~participant) + xlab("Test Time") + ylab("Rhotic Duration (ms)") +
  theme_bw() +
  theme(panel.background = element_rect(fill = "grey79"),
        legend.position = "bottom") + theme(legend.position = "none") + ggtitle("Figure 2: Productions of trills per participant during the pre and post test")
```
