---
title: "Group analysis"
output: pdf_document
---

This document is a group analysis of the impact of training on the duration of taps and trills in Spanish 1 students (6 total).
The data is analyzed using linear mixed effects models in which the outcome variable was rhotic duration.
The fixed effect predictor was the factor *time* (pre and post test) and the models also included a random intercept per participant to take into account the nested structure of the data.
Nested model comparisons were carried out to assess main effects and interactions.
Normality of residuals were assessed by a visual inspection of Q-Q plots in each model.
All analyses were run in R. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(here)
library(tidyverse)
library(janitor)
library(fs)
library(lme4)
library(lmerTest)
```

```{r, include=FALSE}
# load tidy data 
source(here("scripts", "00_helpers.R"))
source(here("scripts", "05_load_data.R"))
```

```{r, include=FALSE}
# filter data to get only taps for Spanish 1 students 
srt_101_tap = srt %>% 
  filter(level == "sp1") %>% 
  filter(is_trill == "tap") %>% 
  filter(!is.na(duration))

srt_101_trill = srt %>% 
  filter(level == "sp1") %>% 
  filter(is_trill == "trill") %>% 
  filter(!is.na(duration))
```


```{r}
srt_101_trill$duration = as.numeric(srt_101_trill$duration)
srt_101_tap$duration = as.numeric(srt_101_tap$duration)
# Do nested model comparisons to determine 
# whether a main effect for time exists 

null_mod_tap_sp1 = lmer(duration ~ 1 + 
                          (1 | participant), 
                        data = srt_101_tap)


time_mod_tap_sp1 = lmer(duration ~ time + 
                          (1 | participant), 
                        data = srt_101_tap)

anova(null_mod_tap_sp1, time_mod_tap_sp1)

qqnorm(resid(time_mod_tap_sp1))
```


```{r}
null_mod_trill_sp1 = lmer(duration ~ 1 + 
                          (1 | participant), 
                        data = srt_101_trill)



time_mod_trill_sp1 = lmer(duration ~ time + 
                          (1 | participant), 
                        data = srt_101_trill)

anova(null_mod_trill_sp1, time_mod_trill_sp1)


fixef(time_mod_trill_sp1)


qqnorm(resid(time_mod_trill_sp1))
```

```{r}
srt_101_tap %>% 
  ggplot(aes(x = duration, y = time)) + geom_boxplot()
```

```{r}
srt_101_trill %>% 
  ggplot(aes(x = duration, y = time)) + geom_boxplot()
```

```{r}
summary(time_mod_trill_sp1)
```